Without loss of generality, \\ any reduced ring is a field

### 2020-04-02 paper-herrsching2019/main.tex
Rules for first-order logic

    \textnormal{double rule for existential quantification} \\\smallskip
    \phantom{a}\hfill
    \Axiom$\varphi \ \fCenter\seq{\vec x, y} \psi$
    \doubleLine
    \UnaryInf$\exists y\?Y\_\! \varphi\ \fCenter\seq{\vec x} \psi$
    \DisplayProof
    \makebox[0pt]{\shifttext{\tiny ($y$ not free in~$\psi$)}}
    \hfill\phantom{a}
    \bigskip

@@

\begin{remark}The case of the locale of surjections~$\NN \twoheadrightarrow
\RR$ is slightly different in that there, even the strong existence axioms of
classical mathematics do not suffice to materialize a point.
\end{remark}

@@

The principal properties of the sheaf semantics is that it is monotone, local
and sound with respect to intuitionistic first-order logic:

@@

XXX include rules for geometric logic?

>>>>

    \textnormal{double rule for existential quantification} \\\smallskip
    \phantom{a}\hfill
    \Axiom$\varphi \ \fCenter\seq{\vec x, y} \psi$
    \doubleLine
    \UnaryInf$\exists y\?Y\_ \varphi\ \fCenter\seq{\vec x} \psi$
    \DisplayProof
    \makebox[0pt]{\shifttext{\tiny ($y$ not free in~$\psi$)}}
    \hfill\phantom{a}
    \bigskip

@@

\begin{remark}The case of the locale of surjections~$\NN \twoheadrightarrow
\RR$ is particular in that there, even the strong existence axioms of
classical mathematics do not suffice to materialize a point. In fact, already
the law of excluded middle or the countable axiom of choice preclude the
existence of points.
\end{remark}

@@

The principal properties of the sheaf semantics is that it is monotone, local
and sound with respect to intuitionistic first-order logic (which we fix for
concreteness in Table~\ref{table:first-order-logic}):

{\makeatletter
\newcommand*{\shifttext}[1]{%
  \settowidth{\@tempdima}{#1}%
  \makebox[\@tempdima]{\hspace*{\@tempdima}#1}%
}
\makeatother
\begin{table}[t]
  \tbl{The rules of intuitionistic first-order logic}{\begin{minipage}{0.8\textwidth}
    \centering
    \medskip

    (structural rules and rules for~${=}\ {\top}\ {\wedge}\ {\bot}\ {\vee}\
    {\exists}$ as in Table~\ref{table:geometric-logic})
    \medskip

    \textnormal{double rule for implication} \\\smallskip
    \phantom{a}\hfill
    \Axiom$\varphi \wedge \psi\ \fCenter\seq{\vec x} \chi$
    \doubleLine
    \UnaryInf$\varphi\ \fCenter\seq{\vec x} \psi \Rightarrow \chi$
    \DisplayProof
    \phantom{a}\hfill
    \bigskip

    \textnormal{double rule for universal quantification} \\\smallskip
    \phantom{a}\hfill
    \Axiom$\varphi \ \fCenter\seq{\vec x, y} \psi$
    \doubleLine
    \UnaryInf$\varphi\ \fCenter\seq{\vec x} \forall y\?Y\_ \psi$
    \DisplayProof
    \makebox[0pt]{\shifttext{\tiny ($y$ not free in~$\varphi$)}}
    \hfill\phantom{a}
    \bigskip

  \end{minipage}}
  \label{table:first-order-logic}
\end{table}}

@@
